\section{Criteria}

The purpose of this section is to review the mandatory, optional and demarcation criteria of \mamid developed
in the functional specification.

Successfully met criteria is marked a checkmark and an optional note:\\
\done[optional remark in green color.]

Criteria not met is marked with a red \textit{x mark} and an optional note:\\
\notdone[optoinal remark in red color.]

Additional features are listed in a separate subsection.

\subsection{Mandatory Criteria}
\subsubsection{Cluster Description by Administrator}
% TODO analyze whether the given criteria can be phrased more abstractly \& move the details to (new) functional requirements. (-> forward 
%lookup references from criteria to functional requirement if required)
\begin{description}
	
	\oitem{MC}{} The administrator interacts with \mamid through a web GUI. \done
	
	% inventory ops
	\oitem{MC}{inventory_definition} The master maintains a list of slaves. \done
	\begin{description}
		\oitem{MC}{} The GUI visualizes the list of Slaves. \done
		\oitem{MC}{} The administrator can add Slaves to the list. \done
		\oitem{MC}{} The administrator can remove a Slave that does not host any MongoDB processes from the 
		list. \done
		\oitem{MC}{spec_risk_groups} The administrator can model a shared risk of failure between hosts, e.g. a shared power 
		supply. \done
		\oitem{MC}{available_slave_types} The administrator can specify whether the Slave has persistent (typically HDD-/SSD-backed) or 
		volatile (RAM-backed) storage. \done
		\oitem{MC}{root_data_directory} The administrator can specify in which filesystem directory on the host the Slave 
		and its MongoDB processes store data. \done[Done as commandline parameter for the slave.]
		% inventory ops -> Slave
		\oitem{MC}{slave_mode_active} The administrator can announce to \mamid that a Slave is ready to host MongoDB processes. 
		\done
		\oitem{MC}{slave_mode_maintenance} The administrator can announce to \mamid that a Slave is under maintenance to inhibit 
		automatic reconfiguration of its MongoDB processes. \done % TODO discuss
		\oitem{MC}{slave_mode_disabled} The administrator can announce to \mamid that a Slave should not host any MongoDB processes. 
		\done
	\end{description}
	
	% Replica Set ops
	\oitem{MC}{replica_set_create} The administrator can describe a new MongoDB Replica Set by specifying constraints on 
	how it should be configured by \mamid. \done
	\begin{description}
		\oitem{MC}{replica_set_config_profiles} The administrator can --- on creation of a Replica Set 
		(\ref{MC:replica_set_create}) --- specify that it must be usable as a configuration server for MongoDB sharding. 
		\done
		\oitem{MC}{replica_set_member_total_counts} The administrator can select the number of MongoDB instances (members) of a 
		Replica Set. \done
		\oitem{MC}{replica_set_member_pv_counts} Volatile and persistent member count of a Replica Set can be independently 
			configured, under constraints described in \textit{\textbf{F210}}. \done
	\end{description}
	\oitem{MC}{} The GUI visualizes the list of configured Replica Sets. \done
	\oitem{MC}{} The administrator can destroy a Replica Set. \done
	
\end{description}

\subsubsection{MongoDB Configuration \& Monitoring}
\begin{description}
	\oitem{MC}{mongod_deployment1} \mamid asserts that the Replica Sets described by the administrator are configured on the cluster 
	(see \ref{MC:replica_set_create}). \done
	\oitem{MC}{mongod_deployment2} To achieve \ref{MC:mongod_deployment1}, \mamid spawns \& controls MongoDB processes on the hosts 
	using a Slave process. \done
	\begin{description}
		\oitem{MC}{mongod_redeployment} \mamid redeploys configured MongoDB processes to hosts where the Slave process reports 
		a situation different from what is expected by the master. \done
		\oitem{MC}{mongod_redeployment_powercycle_specific} Specifically, a host with volatile data storage can lose all data originating 
		from the Slave process or MongoDB and is automatically redeployed with correctly configured MongoDB instances 
		(\ref{MC:mongod_deployment2}). \done
	\end{description}
	% Todo old \oitem{MC}{} The master deploys the Replica Set configuration described by the administrator to the cluster.
	
	% monitoring features
	\oitem{MC}{detect_slave_unexpected_behavior} \mamid detects when a Slave in the inventory behaves unexpectedly, e.g. when 
	it becomes unreachable and the administrator did not announce maintenance to \mamid beforehand. \done
	\oitem{MC}{} \mamid informs the administrator by e-mail about problems in the cluster 
	(\ref{MC:detect_slave_unexpected_behavior}). \done
	\oitem{MC}{} The GUI visualizes Slaves behaving unexpectedly (\ref{MC:detect_slave_unexpected_behavior}). \done
\end{description}

\subsection{Optional Criteria}\label{OptionalCriteria}
\begin{description}
	
	% master
	\oitem{OC}{api_authentication} \mamid requires authentication from the user for all operations.
		\done[Implemented using TLS client certificates issued/signed by a CA. Optional CLI flag for the master.]
	
	% inventory
	\oitem{OC}{manual_autodiscovery} \mamid auto-discovers new Slaves on the administrator's request. \notdone
	\oitem{OC}{continuous_autodiscovery} \mamid continuously auto-discovers new Slaves. \notdone
	\oitem{OC}{monitor_icmp} \mamid recognizes when the Slave software does not respond but the corresponding host is still 
	connected to the network.  \notdone
	\oitem{OC}{export_import_snapshot} The administrator can back up and restore the cluster description. \done[Possible with 
		PostgreSQL's \codeinline{pg\_dump(8)} utility.]
	% Slaves
	\oitem{OC}{tweak_performance_parameters} The administrator can customize performance-relevant parameters of MongoDB 
	processes. \notdone
	
	% automatic repair
	\oitem{OC}{auto_repair} \mamid supports automatic reconfiguration when detecting unexpected behavior of Slaves. The failing 
	Slave is marked as unsuitable to host MongoDB processes and redeployment is triggered to repair the degraded Replica 
	Set (extends \ref{MC:detect_slave_unexpected_behavior}). \notdone
	
	% Replica Sets
	\oitem{OC}{deploy_arbiters} \mamid deploys MongoDB arbiters for configured Replica Sets as needed, removing the 
		restriction to an odd count of Replica Set members.
		\notdone[even member counts without arbiter did not appear to be problematic in test setups.]
	\oitem{OC}{extended_monitoring} \mamid supports extended monitoring of hosts, i.e. metrics beyond the processes managed by \mamid.  
	\notdone
	
	% other
	\oitem{OC}{} The administrator can interact with \mamid via a CLI.  \notdone
	\oitem{OC}{http_api} The administrator can interact with \mamid via a stable, documented HTTP API. \done
\end{description}

\subsection{Demarcation Criteria}
\begin{description}
	\oitem{DMC}{} The administrator does not directly configure individual MongoDB instances spawned \& controlled by \mamid. 
	All configuration happens through \mamid, either automatically (e.g. Replica Set deployment) or through a \mamid interface (e.g. 
	GUI, CLI, HTTP API). \done[In case a Replica Set is not able to elect a primary member, administrative intervention may be required]
		\oitem{DMC}{} \mamid does not deploy MongoDB query routers.  \done
	\oitem{DMC}{} \mamid deploys neither the operating system nor other required software (such as MongoDB binaries) to the 
	cluster hosts.  \done
\end{description}

\subsection{Additional Features}

The following features were added during the implementation phase:

\begin{description}
		\oitem{AF}{} \mamid configures Mongods \& Replica Sets to use \textit{internal authentication} with key files. \done
		\oitem{AF}{} \mamid configures a management user on the Replica Sets to remove the Mongod \textit{localhost} exception
			and enable user access control. \done
		\oitem{AF}{} \mamid supports TLS for communication between master and slave. \done
		\oitem{AF}{} \mamid provides prepared command-lines and MongoDB URLs for further usage of the created Replica Sets. \done
		\oitem{AF}{} \mamid provides helper scripts for creating a x.509 certificate authority and signing certificates with it. \done
\end{description}

