\section {Formatting \& Legend}\label{legend}

% NOTE Declaring the current package
\renewcommand{\gocurpackage}{legend}

This is some text about the package.

\struct{AStruct}{
    Overall description of \refgo{legend.AStruct}.
  
    Multi-paragraph descriptions are supported.
}{
    \property{variable}[Type]{The description of the struct's field \emph{variable}}
    \property{fieldtwo}[Type2]{
      The description of the struct's field \refgo{legend.AStruct.fieldtwo}.
  
      Multi-paragraph (\textbackslash long) descriptions are supported.
    }
}{
    \method{Methodname}[ReturnType]{Method without parameters}
    \method{Methodname2}[ReturnType](%% NOTE the parentheses ()
        \param{pname}[ParamType]{Description of the parameter}
        \param{p2name}[ParamType]{
          Description of the parameter.
          Cannot be multi-paragraph. 
        }
    ){
        Description of the method \refgo{legend.AStruct.Methodname2}.
        
        We can \emph{reference} parameters using absolute identifiers \refgo{legend.AStruct.Methodname2.pname} or relative identifiers \refgoparam{p2name}.
    }
}

\interface{AnInterface}{
  Overall description of the Interface. An interface has no field, hence there is no section for fields.

  Multi-paragraph descriptions are supported. References to other types, e.g. \refgo{legend.AStruct} are possible.
}{
  \method{Methodname}[ReturnType]{Method without parameters}
  \method{Methodname2}[ReturnType]( %% NOTE the parentheses ()
    \param{pname}[ParamType]{Description of the parameter}
    \param{p2name}[ParamType]{
      Description of the parameter.
      Cannot be multi-paragraph. 
    }
  ){
    Description of the method \refgo{legend.AnInterface.Methodname}.
   
    Multi-paragraph descriptions are supported.

    Referencing the package: 
    \refgo{legend}
  
    Referencing the interface: 
    \refgo{legend.AnInterface}
  
    Referencing the interface variable: 
    \refgo{legend.AnInterface.variable}
  
    Referencing the method: 
    \refgo{legend.AnInterface.Methodname2}
  
    Referencing the method parameter: 
    \refgo{legend.AnInterface.Methodname2.pname}



  }
}

